\title{TU project proposal template}
\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{glossaries}
\usepackage{pdfpages}

\makeglossaries
\include{acro}

\begin{document}

\pagenumbering{roman}
\include{coverpage}
\include{titlepage}

\section*{Certificate of approval}
\addcontentsline{toc}{section}{Certificate of approval}
\par
The undersigned certify that the final year project entitled \textbf{”Title"} submitted by \textbf{Members} to the Department of Electronics , Communication and Computer Engineering in partial fulfillment of requirement for the degree of Bachelor of Engineering in Electronics and Computer Engineering. The project was carried out under special supervision and within the time frame prescribed by the syllabus. We found the students to be hardworking, skilled, bonafide and ready to undertake any commercial and industrial work related to their field of study and hence we recommend the award of Bachelor of Electronics and Communication Engineering degree.
\par
We found the students to be hardworking, skilled, bonafide and ready to undertake any commercial and industrial work related to their field of study and hence we recommend the award of Bachelor of Computer Engineering degree.\\[1cm]
1. ................. \\
Dr  \\
(Project Supervisor) \\[1cm]
2. ................. \\
Name:............... \\
(External Examiner) \\[1cm]
3. ................. \\
Dr  \\
Head of Department
\clearpage

\section*{Copyright}
\addcontentsline{toc}{section}{Copyright}
The author has agreed that the library, IOE Central Campus Pulchowk may make this report freely available for the inspection. Moreover, the author has agreed the permission for the extensive copying of this project report for the scholarly purpose may be granted by supervisor who supervised the project work recorded herein or, in his absence the Head of The Department wherein the project was done. It is understood that the recognition will be given to the author of the report and to the Department of Electronics and Computer Engineering, IOE Central Campus Pulchowk in any use of the material of this project report. Copying or publication or other use of this report for financial gain without approval of the department and author's written permission is prohibited. Request for this permission to copy or to make any other use of material in this report in whole or in part should be addressed to: \\[1cm]
Head of Department \\
Department of Electronics and Computer Engineering \\
IOE Central Campus Pulchowk\\
Pulchowk,\\
Lalitpur, Nepal
\clearpage

\section*{Acknowledgment}
\addcontentsline{toc}{section}{Acknowledgment}
\par
We would like to express our heartfelt gratitude to Department of Electronics and Computer Engineering of Institute of Engineering, Pulchowk Campus for constructing arena for exchange of knowledge and personal creativity development. All the mentors and the resources provided by the College has been crucial in our vision that we present today. Projects are at the heart of engineering and development of the society. This projects will build necessary maturity to handle real world projects in the future.
\par
We would like to extend our gratitude to \textbf{Dr ..}, \textbf{Dr ...} and \textbf{...} for providing us with all the necessary guidance and help to come in this stage. \\[1cm]
\clearpage

\section*{Abstract}
\par

\addcontentsline{toc}{section}{Abstract}
\clearpage

\tableofcontents
\addcontentsline{toc}{section}{Table of contents}
\clearpage

\listoftables
\addcontentsline{toc}{section}{List of tables}
\clearpage

\listoffigures
\addcontentsline{toc}{section}{List of Figures}
\clearpage

\printglossary[type=\acronymtype,title=List of Symbols and Acronym]
\addcontentsline{toc}{section}{List of Symbols and Acronyms}

\clearpage

\pagenumbering{arabic}
\section{Introduction}

\par

\clearpage

\appendix
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
\clearpage
\nocite{*}


\clearpage
\bibliographystyle{plain}
\bibliography{source}
\addcontentsline{toc}{section}{References}

\end{document}
